\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Christopher,
    lastname=Celaya,
    email=chris@chriscelaya.com,
    phone=915-270-0237,
    % linkedin=christophercelaya,
    github=while-basic,
    city=El Paso,
    state=TX,
    qrcode=./images/qr.png
]

\objective{Industrial Technician with expertise in AI/ML Engineering, specializing in intelligent
automation, predictive maintenance, and industrial data analytics. 11+ years of experience in
manufacturing environments, troubleshooting electrical and mechanical systems, and optimizing
operations. Excited about leveraging technology to improve efficiency, reduce downtime, and enhance
decision-making in smart factories.}

% ----- Work Experience -----
\section{Work Experience}

\experience{T5 Data Centers}{%
    \role{Critical Facilities Data Center Technician II}{Sept 2021 - June 2022}{
        \achievement{Maintain and operate both critical and non-critical data center infrastructure, equipment, and systems.}
        \achievement{Achieved 100\% uptime for critical infrastructure by leading PM's on systems utilizing CMMS.}
        \achievement{Supervise external contractors, ensuring adherence to critical facility workplace rules.}
    }
}

\experience{CN Wire}{%
    \role{Electro-Mechanic}{Jan 2018 - Sept 2021}{
        \achievement{Enhanced equipment reliability through troubleshooting electrical systems, HMI panels, and sensors.}
        \achievement{Maintain a number of cooling, compression and emulsion systems required for facility operations.}
        \achievement{Install, maintain, and troubleshoot electrical components and equipment for process equipment.}
    }
}

\experience{Schneider Electric}{%
    \role{Wiring Technician | Quality Assurance}{May 2016 - Dec 2017}{
        \achievement{Improved quality by 20\% by overseeing testing/assembly of electrical panels and resolving defects.}
        \achievement{Interpret point-to-point diagrams, bill of materials, and wiring schematics.}
        \achievement{Oversee testing and assembly of low voltage electronic products.}
    }
}

\experience{Delfingen}{%
    \role{Maintenance Technician}{Dec 2015 - Dec 2016}{
        \achievement{Manage maintenance on equipment, including extrusion, pneumatic, hydraulic, water, and electrical.}
        \achievement{Carry out tasks including equipment repair, electrical troubleshooting, and preventative maintenance.}
        \achievement{Determine and resolve issues with corrugated screws, cutters, pullers, and printing systems.}
        \achievement{Complete additional duties such as welding, fabrication, including building maintenance.}
    }
}

\experience{Dal-Tile}{%
    \role{Maintenance Technician III}{Feb 2013 - Oct 2015}{
        \achievement{Install and maintain hydraulic press, electrical panels and mechanical components.}
        \achievement{Acknowledge machine malfunctions, install electro-mechanical valves, and perform routine maintenance.}
        \achievement{Carry out additional routine maintenance on raw material conveyors, dust, compression, and cooling systems.}
        \achievement{Operate industrial hydraulic systems, serve oil changes, and routine die-block quality checks.}
        \achievement{Manage materials processing and storage, including silos, conveyors, spray dryers, ball mills, and vibrating screens.}
    }
}

% ----- Technical Projects -----
\section{Technical Projects}

\project{Medchat}{AI/ML Medical LLM}{
    \achievement{Developed a web application for healthcare professionals with accurate diagnoses.}
    \achievement{Technologies Used: \tech{Python}, \tech{Next.js}, \tech{Tailwind CSS}}
}

\project{Minecraft AI Bot}{LLM}{
    \achievement{Trained LLM using real-world game data to build autonomously, reducing intervention by 95\%.}
    \achievement{Technologies Used: \tech{JavaScript}, \tech{Python}, \tech{Google Colab}, \tech{Minecraft}, \tech{Reinforcement Learning}}
}

\project{Gemini Pro Vision}{AI/ML Computer Vision, Full-Stack}{
    \achievement{Developed a chatbot with real-time vision and text-to-speech capabilities using machine vision.}
    \achievement{Technologies Used: \tech{JavaScript}, \tech{Next.js}, \tech{Tailwind CSS}, and \tech{Gemini API}}
}

\project{chriscelaya.com}{Web Development}{
    \achievement{Designed a personal portfolio website using Next.js. Features resume, experience, and projects.}
    \achievement{Technologies Used: \tech{Next.js}, \tech{JavaScript}, \tech{Vercel}, and \tech{Supabase}}
}

\project{Midi Saber}{Game Development, VR, Web Development}{
    \achievement{Created a MIDI-powered interface to generate beat maps for Beat Saber using a MIDI drum pad.}
    \achievement{Technologies Used: \tech{JavaScript}, \tech{Unity}, \tech{Novation}, and \tech{Beat Saber}}
}

% ----- Education -----
\section{Education}

\degree{Bachelor of Science in Electrical Engineering}{University of Texas at El Paso}{GPA: 3.5/4.0}{
    \achievement{Focus in Fields and Devices - Incomplete} 
}   

\degree{Bachelor of Science in Computer Science}{El Paso Community College}{GPA: 3.7/4.0}{
    \achievement{Focus in Cyber Security - Incomplete}
}

% ----- Skills -----
\section{Skills}

\begin{itemize}
    \item \textbf{Software Development:} Python, C, JS, TS, Next.js, React.js, Tailwind, TensorFlow, Java, Pytorch
    \item \textbf{Databases \& Tools:} Docker, SQL, MongoDB, PostgreSQL, Redis, Azure, AWS, Blockchain
    \item \textbf{Industrial Infrastructure:} Preventative Maintenance, CMMS, HMI, SCADA, Machine Vision
    \item \textbf{Leadership \& Management:} Team Training, Workflow Optimization, Process Improvement
    \item \textbf{AI/ML Training \& Development:} CUDA, HuggingFace, Kaggle, Google Colab
    \item \textbf{Hardware:} NVIDIA H100s \& A100s for large language model training
\end{itemize}

% ----- Certifications -----
\section{Certifications}

\begin{itemize}
    \item NFPA 70E | Electrical Safety
    \item OSHA 10 | Construction Safety
\end{itemize}

\end{document}
